### 2017-10-13 Gruba/02-overview.tex

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally created (0) by $O$.
\end{definition}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=.67\linewidth]{figures/architecture.pdf}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-4ex}
\end{figure}

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
%\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers over \\
\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., $\frac{\#R_u}{\#E_u}$ \\  \midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-3ex}
\end{table}
\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
%\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-2ex}
\end{table}

>>>>

\begin{definition}
\label{def:blog}
A microblog $M_b = (O, T, M, flag)$ has its owner $O$ (a.k.a. user in this paper) to whom $M_b$ belongs (either created or \retd{}), the generated time $T$ of $M_b$, the message context $M$, and $flag$ denoting $M_b$ is \retd{} (1) or originally \tw{} (0) by $O$.
\end{definition}

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=.67\linewidth]{figures/architecture.eps}
\vspace{-1ex}
\caption{\sys{} Architecture}
\label{fig:framework}
\vspace{-4ex}
\end{figure}

@@

\begin{table}[tb!]
\centering
\begin{small}
\caption{Illustration of Variables in Basic Feature}
%\vspace{0.3cm}
\label{tbl:fe-info}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Variables}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
$G_u$				& gender of user $u$				\\	\midrule
$P_u$				& province of user $u$				\\	\midrule
\#$R_u$				& number of followers				\\	\midrule
\#$E_u$				& number of followees				\\	\midrule
                    & a ratio defined as the number of followers over \\
\raisebox{1.5ex}{$R_{ee}$}  & that of followees, i.e., ${\#R_u}/{\#E_u}$ \\  \midrule
$U_t$					& user type (as detailed in Table \ref{tbl:ucate})			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

\begin{table}[tb!]
\centering
\begin{small}
\caption{Category of User Type}
%\vspace{0.3cm}
\label{tbl:ucate}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{l}{\textbf{Values}} & \multicolumn{1}{l}{\textbf{Illustration}}	\\	\midrule \midrule
0                       & $\#E_u \le 50 \ {\bf and} \ \#R_u \le 50$				\\	\midrule
\multirow{2}{*}{1}      & \multirow{2}{*}{$\frac{\#E_u}{\#R_u} \ \ge 5$}	\\
 						&                       									\\	\midrule
\multirow{2}{*}{2}		& \multirow{2}{*}{$\frac{\#R_u}{\#E_u} \ \ge 5$}  \\
						&															\\	\midrule
3                   	& other cases 												\\ \bottomrule
\end{tabular}
\end{small}
\vspace{-2ex}
\end{table}
